Universal Anonymous Signatures

### 2022-05-04 prism-backend/research/gsac/app-building-blocks.tex
Updated SBCM definition, and gen constructions of UAS and GSAC accordingly. SBCM proofs pending.

\subsection{Signatures over Blocks of Messages}
\label{sapp:sbm}

\todo{Intro to \SBM (CL,BBS+,PS...)}

To the best of our knowledge, models of existing schemes for signing blocks of
messages like \cite{cl02,asm06,ps16} target precisely the case of signing blocks
of \emph{plain} messages, as described in \appref{sapp:sbm}. However, for our
generic constructions, we need interactive signing protocols between a user
and a signer, where the user has a block of messages to sign blindly, and both
receive a common block of messages to be also included in the resulting
signature. This is precisely the case of partially blind signatures, that
collapse to blind signatures when there is no common message between user
and signer; and to conventional signatures when the user does not input a
message to be blindly signed \cite{ao00}. Partially blind signatures, as
blind signatures \cite{ps96}, cannot be modelled with the conventional security
against existential forgeries. Simply because the user is actually expected to
be able to create signatures on messages unknown to the signer, which formally
translates into the impossibility to check whether a signature output by the
adversary is over a message that has been queried to the signing oracle or not.
Instead of using the conventional existential unforgeability property,
(partially) blind signature schemes move to the ``one-more'' paradigm, which
demands that no adversary can produce $n+1$ signatures after having interacted
with the signing oracle at most $n$ times.

Informally, the mentioned \SBM schemes \cite{cl02,asm06,ps16} and related works
\cite{cdl16b} \todo{check} describe ways to support signing committed blocks of
messages. But do not give security models of the resulting construction, nor
of course prove its security. As we aim at using this variant as a generic
building block, we give a formal model of such extension, that we call
Signatures over Blocks of Committed Messages (\SBCM), from a generic \SBM model.
The algorithms composing an \SBCM scheme are as follows:

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \Ssecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
  parties with shared input a block of messages \smsg. The party running
  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
  block-committed and then signed along with \smsg. The party running \SBCMSign
  controls the signing key \SBCMsk. As a result, both parties get signature
  \SBCMsig over $\smsg \cup \overline{\smsg}$.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\widetilde{\smsg})$.] Checks
  whether \SBCMsig is a valid signature over the set of messages
  $\widetilde{\smsg}$ (independently on whether the messages where signed as
  commitments or not), under verification key \SBCMvk.
\end{description}

\paragraph{Correctness.} %
Informally, an \SBCM scheme is correct if signatures generated between an honest
party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
honest signer running \SBCMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
accepted by \SBCMVerify.

    \procedure{$\ExpSBCMOMF(\SBCMsecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      ((\sig_1,\smsg_1),\dots,(\sig_{n+1},\smsg_{n+1})) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,\smsg_i) = 0:
      \pcreturn 0 \\
      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j: \pcreturn 0 \\
      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
      \textrm{was called more than $k$ times}: \pcreturn 0 \\
      \pcreturn 1 \\
    }

\subsubsection{From EUF-secure \SBM schemes to OMF-secure \SBCM
  schemes} %
\todo{Describe and prove.}

@@

>>>>

@@

\iffalse
\subsection{Signatures over Blocks of Messages}
\label{sapp:sbm}

A signature scheme on blocks of messages (\SBM) allows a signer to create a
single signature over a set of messages. The resulting signature is typically
more concise than just creating multiple signatures, and typical schemes
\cite{cl02,asm06,ps16} are additionally compatible with efficient proof
protocols over the signed messages. The functionality offered by an \SBM scheme
is as follow:

\begin{description}
\item[$\SBMparm \gets \SBMSetup(\SBMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBMsecpar.
\item[$(\SBMvk,\SBMsk) \gets \SBMKeyGen(\SBMparm)$.] Generates a
  verification-signing key pair.
\item[$\SBMsig \gets \SBMSign(\SBMsk,\smsg)$.] Produces a signature \sig, over
  a block of messages \smsg, using signing key \SBMsk.
\item[$1/0 \gets \SBMVerify(\SBMvk,\SBMsig,\widetilde{\smsg})$.] Checks
  whether \SBMsig is a valid signature over the set of messages \smsg, under
  verification key \SBMvk.
\end{description}

An \SBM scheme must satisfy correctness and unforgeability properties.

\paragraph{Correctness.} %
Informally, an \SBM scheme is correct if signatures generated between an honest
party running running \SBMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
accepted by \SBMVerify.

\paragraph{Unforgeability.} %
It must be unfeasible for an adversary to produce signatures over blocks of
messages that have not been signed by the signer. More formally, an \SBM scheme
is unforgeable if, for all p.p.t. adversaries $\adv$, $\Pr[\ExpSBMEUF
(\SBMsecpar) = 1]$, as defined in \figref{fig:sbm-games}, is a negligible
function of the security parameter.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering    
    \procedure{$\ExpSBMEUF(\SBMsecpar)$}{%
      \SBMparm \gets \SBMSetup(\SBMsecpar) \\
      (\SBMvk,\SBMsk) \gets \SBMKeyGen(\SBMparm) \\
      (\SBMsig,\smsg) \gets \adv^{\SSign(\SBMsk,\cdot)}(\SBMvk) \\
      \pcif \SBMVerify(\SBMvk,\SBMsig,\smsg) = 0: \pcreturn 0 \\
      \pcif \smsg~\textrm{was not queried to \SBMSign}: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:sbm-games}
  \caption{Unforgeability game for \SBM schemes.}
\end{figure}
\fi

For our generic constructions, we use interactive signing protocols between a
user and a signer, where the user has a block of messages to sign blindly, and
both receive a common block of messages to be also included in the resulting
signature. This is precisely the case of partially blind signatures, that
collapse to blind signatures when there is no common message between user
and signer; and to conventional signatures when the user does not input a
message to be blindly signed \cite{ao00}. Partially blind signatures, as
blind signatures \cite{ps96}, cannot be modelled with the conventional security
against existential forgeries. Simply because the user is actually expected to
be able to create signatures on messages unknown to the signer, which formally
translates into the impossibility to check whether a signature output by the
adversary is over a message that has been queried to the signing oracle or not.
Thus, instead of using the conventional existential unforgeability property,
(partially) blind signature schemes move to the ``one-more'' paradigm, which
demands that no adversary can produce $n+1$ distinct signatures after having
interacted with the signing oracle at most $n$ times.

To the best of our knowledge, models of existing schemes for signing blocks of
messages like \cite{cl02,asm06,ps16,cdl16b} target the case of signing blocks
of \emph{plain} messages, and are subsequently informally extended to support
signing commitments to blocks of messages via interactive protocols. However,
they do not support signing both committed and plain messages (although the
extension is trivial); and, more importantly, do not give security models of
the resulting construction, nor of course prove its security. While the
extension seems straightforward, the modelling needs to be changed due to the
mentioned nuance of the conventional EUF notion not being compatible with
interactive signing protocols where the signer does not learn (some of) the
signed message(s). As we aim at using this variant as a generic building block,
we briefly model such a scheme for Signatures over Blocks of Committed Messages
(\SBCM).

The syntax for an \SBCM scheme is as follows:

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBCMsecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
  parties with shared input a block of messages \smsg. The party running
  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
  block-committed and then signed along with \smsg. The party running \SBCMSign
  controls the signing key \SBCMsk. As a result, both parties get signature
  \SBCMsig over $\smsg \cup \overline{\smsg}$.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.] Checks
  whether \SBCMsig is a valid signature over the set of messages
  $\overline{\smsg}$ and \smsg, under verification key \SBCMvk.
\end{description}

\paragraph{Correctness.} %
Informally, an \SBCM scheme is correct if signatures generated between an honest
party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
honest signer running \SBCMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\overline{\smsg}$ and \smsg that is
accepted by \SBCMVerify.

    \procedure{$\ExpSBCMOMF(\SBCMsecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      ((\sig_1,\overline{\smsg}_1, \smsg_1),\dots,
      (\sig_{n+1},\overline{\smsg}_{n+1},\smsg_{n+1})) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,
      \overline{\smsg}_i,\smsg_i) = 0: \pcreturn 0 \\
      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j \land
      \overline{\smsg}_i = \overline{\smsg}_j: \pcreturn 0 \\
      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
      \textrm{was called more than $k$ times}: \pcreturn 0 \\
      \pcreturn 1 \\
    }

\subsection{An Instantiation of \SBCM with BBS+}

Next, we give an instantiation of an \SBCM scheme, based on BBS+ signatures.
We emphasize again that this is essentially equivalent to the protocol for
signing committed block of messages in \cite{asm06} and, also, to the equivalent
ones in \cite{cl02,ps16} (although not for BBS+ signatures). The main difference
being that we allow merging committed blocks of messages and blocks of
(plaintext) messages into the same signature.
%
Note also that, in our instantiation, we just include a generic \NIZK, for some
relation over witness $\overline{\smsg}$ (i.e., the messages to be blindly
signed), and statement $(\Ccom,\smsg)$ (i.e., their block commitment, and the
plainly signed messages). This is intentional, as we want to support cases where
proving arbitrary predicates is possible (as opposed to ``just'' proving that
the commitment is over the messages in $\overline{\smsg}$).
%
When we want to make explicit the relation over which the employed \NIZK is
defined, we add a $\NIZKRel$ superscript to the algorithms.

\paragraph{$\SBCMparm \gets \SBCMSetup(\SBCMsecpar,\nattrs,\tnattrs)$.} %
Generates a bilinear group $\BB = (p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e)
\gets \PGen(\SBCMsecpar)$, and $\nattrs+\tnattrs+1$ additional generators
$\gen{g}$, $\gen{h}_1,...,\gen{h}_{\nattrs}$,$\gen{\th}_1,...,\gen{\th}_{\tnattrs}$
of $\GG_1$. Returns $\SBCMparm \gets (\SBCMsecpar,\nattrs,\tnattrs,\BB,
\gen{g},\gen{h}_1,...,\gen{h}_{\nattrs},\gen{\th}_1,...,\gen{\th}_{\tnattrs})$.
We assume that \SBCMparm is available to all other algorithms, even when not
explicitly passed as an argument.

\paragraph{$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.} %
Parses \SBCMparm as $(\cdot,\cdot,(p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e),
\dots$ $\NIZKcrs \gets \NIZKSetup(\secpar)$. Outputs $\SBCMsk \gets \ZZ^*_p$,
and $\SBCMvk \gets (\NIZKcrs,\gen{g}_2^{\SBCMsk})$.

\paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},
  \smsg), \SBCMSign(\SBCMsk,\smsg) \rangle$.} %

\begin{itemize}
\item \underline{User}: If $|\smsg|>\nattrs$ or $|\overline{\smsg}|>\tnattrs$,
  abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
  \gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
  and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
  Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \underline{Signer}: If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify
  (\NIZKcrs,\Ccom,\NIZKproof)$ and return $0$ if it fails. Else, compute
  $x,\tilde{s} \getr \ZZ^*_p, A \gets (\gen{g}_1\Ccom \gen{g}^{\tilde{s}}
  \prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Send
  $(A,x,\tilde{s})$ to User.
\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq
  e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},
  \gen{g}_2)$: return $0$. Else, return $(A,x,s)$.
\end{itemize}

\paragraph{$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.} %
To verify a signature \SBCMsig, for message set $\overline{\smsg}$ that was
signed as a block commitment, and message set \smsg, signed as plaintext, parse
\SBCMsig as $(A,x,s)$ and check if $e(A,\gen{g}_2^x\SBCMvk) =
e(\gen{g}_1\gen{g}^s\prod_{i \in |\overline{\smsg}|}\gen{h}^{\overline{\smsg}_i}
\prod_{i \in |\smsg|}\gen{h}^{\smsg_i},\gen{g}_2)$

\paragraph{Proving Knowledge of Signature.} %
Note that proving knowledge of a BBS+ signature as produced in our \SBCM variant
is essentially the same as in \cite{asm06,cdl16b}, only needing to account for
the different basis for messages signed in committed and plain form.

\subsubsection{Security.} Next, we sketch that the given BBS+ interactive
signing protocol is correct and OMF-secure.

\paragraph{Correctness.} \todo{XXX}

\paragraph{OMF security.} \todo{YYY}

### 2022-05-04 prism-backend/research/gsac/construction-uas.tex
Updated SBCM definition, and gen constructions of UAS and GSAC accordingly. SBCM proofs pending.

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\sipk,\attrs)\rangle$.} %
The protocol is run between an issuer, and a user with secret key \usk and
credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. For readability we write $\attrs_{\scred}$ as abbreviation for
$\lbrace \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for
$\sipk_{\scred}$. The user requests a signature on a commitment to the user key,
as well as on the attributes in \attrs. In addition, the user proves that the
issuance function \fissue established by the issuer is satisfied by the
credentials in $\scred$
and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
(\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom = \CCommit(usk) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,
\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
for a user to obtain a credential from an issuer of the system is as follows:

\begin{itemize}
\item \uline{User}: Commit to the user secret key with $\Ccom \gets
  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
  (\Ccom,\attrs,\sipk_{\scred}))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
  \cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

>>>>

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
The protocol is run between an issuer, and a user with secret key \usk and
credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. For readability we write $\attrs_{\scred}$ as abbreviation for
$\lbrace \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for
$\sipk_{\scred}$. The user requests a signature on a commitment to the user key,
as well as on the attributes in \attrs. In addition, the user proves that the
issuance function \fissue established by the issuer is satisfied by the
credentials in $\scred$
and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
(\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom = \CCommit(usk) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,
\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
for a user to obtain a credential from an issuer of the system is then simply an
execution of the interactive signing protocol of an \SBCM scheme, where the user
runs $\SBCMCom(\ipk,\usk,\attrs)$, and the issuer runs $\SBCMSign(\isk,\attrs)$;
in both cases, using $\NIZKRel_{\Issue}$ as \NIZK relation.

\iffalse
\begin{itemize}
\item \uline{User}: Commit to the user secret key with $\Ccom \gets
  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
  (\Ccom,\attrs,\sipk_{\scred}))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
  \cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}
\fi
